---
title: "Superslides Template"
subtitle: "Super features demo"
authors:
  - name: "Giuseppe Ragusa"
    affiliation: "Sapienza University of Rome"
    orcid: 0000-0002-6964-6278
    email: "giuseppe.ragusa@gmail.com"
  - name: "Giuseppe Ragusa"
    affiliation: "Sapienza University of Rome"
    email: "giuseppe.ragusa@gmail.com"
date: "Rome, 12 October 2025"
date-format: full
date-updated: "October 1, 2025"
format:
    superslides-typst:
        fig-width: 9
        fig-height: 6
editor:
  render-on-save: true
---

```{r}
#| include: false
Sys.setenv(RETICULATE_PYTHON = "~/.pyenv/shims/python3")
```
# Getting Started

## Introduction

::: {.simplebox}
Welcome to **Superslides**! This template demonstrates:

- Enhanced Typst presentations with Touying
- Professional title slides with interactive elements
- Advanced code blocks with zebraw integration
- Simple 3-color customization system

$$
Y_t = A_1 Y_{t-1} + E_t \to \int f(x) dx
$$
:::

## Math

$$
Y_i = X_i\beta + u_i, \quad i=1,\ldots,n
$$

## Features Overview

### Key capabilities

- 🎨 Professional title slides with left-aligned layout
- 🔗 Interactive QR codes and clickable links
- 📝 Enhanced code blocks with mathematical annotations
- 🎯 Simple 3-color palette system
- 🌐 Multi-language support (English/Italian)

#### Note: This is a fourth level header `====`

## Typography

Standard markdown formatting works as expected:

  - _emphasis_ (`_emphasis_`)
  - **bold** (`**bold**`)
  - **_bold emphasis_** (`**_bold emphasis_**`)
  - ~~strikethrough~~ (`~~strikethrough~~`)
  - [alert]{.alert} (`[alert]{.alert}`)
  - [strong]{.strong} (`[strong]{.strong}`)

## Code Blocks

```{r}
#| fig-align: "center"
#| layout-ncol: 2
plot(rnorm(10))
```

##

```{python}
#| layout-ncol: 2
#| fig-cap:
#|   - "Line Plot 1"
#|   - "Line Plot 2"

import matplotlib.pyplot as plt
plt.plot([1,23,2,4])
plt.show()

plt.plot([8,65,23,90])
plt.show()
```
## Code Block Configuration

You can control code block appearance through YAML parameters:

- `raw-font-size: 20pt` - Font size for code blocks
- `raw-inline-size: 20pt` - Font size for inline code
- `raw-inset: 2pt` - Padding around code blocks

## Python Example

```python
def quadratic_formula(a, b, c):
    """Solve quadratic equation ax² + bx + c = 0"""
    discriminant = b**2 - 4*a*c

    if discriminant < 0:
        return None  # No real solutions
    elif discriminant == 0:
        return -b / (2*a)  # One solution
    else:
        sqrt_d = discriminant**0.5
        x1 = (-b + sqrt_d) / (2*a)
        x2 = (-b - sqrt_d) / (2*a)
        return x1, x2
```

## R Statistical Analysis

```r
calculate_statistics <- function(data) {
    n <- length(data)
    mean_x <- sum(data) / n
    variance <- sum((data - mean_x)^2) / (n-1)
    std_dev <- sqrt(variance)
    se <- std_dev / sqrt(n)

    return(list(
        mean = mean_x,
        variance = variance,
        std_dev = std_dev,
        std_error = se
    ))
}
```

## Julia Mathematical Functions

```julia
function fibonacci(n)
    if n <= 1
        return n
    else
        return fibonacci(n-1) + fibonacci(n-2)
    end
end
```

## Inline Code

You can also use `inline code` within text. The font size is controlled by the `raw-inline-size` parameter.

# Table

## Table using R


```{r}
#| label: tbl-iris
#| tbl-cap: First few rows of the iris dataset.
#| tbl-cap-location: bottom
library(tinytable)
## fontsize is in em
tt(head(iris))|> style_tt(fontsize=0.8) |> theme_striped()
```
## Table using R with math

```{r}
library(tinytable)

theme_mitex <- function(x, ...) {
    fn <- function(table) {
        if (isTRUE(table@output == "typst")) {
          table@table_string <- gsub("\\$(.*?)\\$", "#mitex(`\\1`)", table@table_string)
        }
        return(table)
    }
    x <- style_tt(x, finalize = fn)
    x <- theme_striped(x)
    return(x)
}

options(tinytable_html_mathjax = TRUE)
options(tinytable_tt_theme = theme_mitex)
```

```{r}
data.frame(Math = c("$\\alpha$", "$a_{it}$", "$e^{i\\pi} + 1 = 0$")) |>
  tt()
```


# Box and Theorem Systems

## Current Showybox System

Superslides supports two types of showyboxes via the `::: {.classname}` syntax, with colors automatically generated from your primary and secondary colors:

## Simplebox


**Code:**
```markdown
::: {.simplebox}
## Simple Information
This is a simple information box
with blue styling.
:::
```

**Result:**

::: {.simplebox}
## Simple Information
This is a simple information box with blue styling.
:::

##

```
::: {.warningbox}
### Warning
This is a warning box with
red styling for alerts.
:::
```

::: {.warningbox}
### Warning
This is a warning box with red styling for alerts.
:::

# Theorem System


Superslides provides a comprehensive theorem system using Quarto's native syntax with beautiful styling.

## Configuration

The theorem system is configured in the YAML header:

```yaml
theorem-package: "ctheorems"      # Package to use
theorem-lang: "en"                # Language: "en" or "it"
theorem-numbering: true           # Sequential numbering (1, 2, 3...)
# Colors automatically generated from primary-color
```

## Basic Theorem


### Quarto Syntax

```markdown
::: {#thm-main}
### Fundamental Theorem
Every positive integer can be written as a sum of distinct powers of 2.
:::
```


### Result

::: {#thm-main}
### Fundamental Theorem
Every positive integer can be written as a sum of distinct powers of 2.
:::



## Lemma




### Quarto Syntax:
```markdown
::: {#lem-binary}
### Binary Representation
Any positive integer has a unique binary representation.
:::
```

### Result

::: {#lem-binary}
### Binary Representation
Any positive integer has a unique binary representation.
:::



## Assumption


### Quarto Syntax

```markdown
::: {#finite .assumption}
### Finiteness
We assume all sets under consideration are finite.
:::
```

### Result

::: {#finite .assumption}
### Finiteness
We assume all sets under consideration are finite.
:::

## Definition


### Quarto Syntax

```markdown
::: {#def-group}
### Group
A group is a set G with an operation * that satisfies:

- Closure
- Associativity
- Identity element
- Inverse elements
:::
```


### Result

::: {#def-group}
### Group
A group is a set G with an operation * that satisfies:

- Closure
- Associativity
- Identity element
- Inverse elements
:::



## Cross-References

Theorems use Quarto's crossref system with `@label`:

```markdown
The proof follows from @lem-binary to establish @thm-main.
```

**Result:** The proof follows from @lem-binary to establish @thm-main.

For assumptions, use raw Typst syntax `#ref(<label>)`:

```markdown
Under `#ref(<finite>)`{=typst}, the proof follows from @lem-binary.
```

**Result:** Under `#ref(<finite>)`{=typst}, the proof follows from @lem-binary.

##

{{< v -3em >}}

Quarto theorem types plus Assumption are supported:


| Type | Environment | Reference |
|------|-------------|-----------|
| Theorem | `::: {#thm-label}` | `@thm-label` |
| Lemma | `::: {#lem-label}` | `@lem-label` |
| Corollary | `::: {#cor-label}` | `@cor-label` |
| Proposition | `::: {#prp-label}` | `@prp-label` |
| Conjecture | `::: {#cnj-label}` | `@cnj-label` |
| Definition | `::: {#def-label}` | `@def-label` |
| Example | `::: {#exm-label}` | `@exm-label` |
| Exercise | `::: {#exr-label}` | `@exr-label` |
| Solution | `::: {#sol-label}` | `@sol-label` |
| Remark | `::: {#rem-label}` | `@rem-label` |
| Assumption | `::: {#label .assumption}` | `#ref(<label>)` |

# Columns

Superslides supports multi-column layouts with flexible widths, alignment, and background colors.

## Basic Two-Column Layout

:::: {.columns}
::: {.column width="40%"}
**Left Column (40%)**

This is the left column with 40% width. You can include any markdown content here:

- Lists
- Text
- Images
- Code
:::

::: {.column width="60%"}
**Right Column (60%)**

This is the right column with 60% width.

You can have different amounts of content in each column.

$$
\int_0^\infty e^{-x^2} dx = \frac{\sqrt{\pi}}{2}
$$
:::
::::

## Columns with Background Colors

:::: {.columns}
::: {.column width="50%" bg="#e8f4f8"}
**Light Blue Background**

Content with a light blue background using direct hex color: `bg="#e8f4f8"`

This is useful for highlighting specific content or creating visual separation.
:::

::: {.column width="50%" bg="#fff5e6"}
**Light Orange Background**

Content with a light orange background using `bg="#fff5e6"`

Different columns can have different background colors.
:::
::::

## Columns with Height and Background

:::: {.columns}
::: {.column width="50%" bg="#e8f4f8" height="12cm"}
**Fixed Height Column**

This column has a fixed height of 12cm using `height="12cm"`

The background color extends to fill the entire height, creating a nice visual effect that extends toward the end of the slide.
:::

::: {.column width="50%" bg="#fff5e6" height="12cm"}
**Matching Height**

Both columns have the same height, creating a uniform appearance.

You can use various units:
- `height="12cm"` (centimeters)
- `height="15em"` (em units)
- `height="200pt"` (points)
:::
::::

## Columns with Alignment

:::: {.columns align=top}
::: {.column width="50%" align=center bg="#f0f0f0"}
**Centered Content**

This content is centered within the column using `align=center`
:::

::: {.column width="50%" align=left}
**Left-Aligned Content**

- This content is left-aligned
- Default alignment is left
- You can also use `align=right`
:::
::::

## Fixed Width Columns

:::: {.columns align=center totalwidth=25em}
::: {.column width="40%" bg="#e6f3ff"}
**Constrained Width**

These columns use `totalwidth=25em` to constrain the entire block width.
:::

::: {.column width="60%" bg="#fff0f5"}
**Centered Block**

The entire column block is centered on the slide.
:::
::::

## Using YAML Variables for Colors

You can define colors in your YAML frontmatter and reference them:

```yaml
---
primary-bg: "#e8f4f8"
secondary-bg: "#fff5e6"
---
```

Then use them in columns:

```markdown
:::: {.columns}
::: {.column width="50%" bg="primary-bg"}
Content using primary-bg variable
:::
::: {.column width="50%" bg="secondary-bg"}
Content using secondary-bg variable
:::
::::
```

This allows for consistent theming across your presentation.

## Full-Height Columns

Use `fullheight="true"` on the columns container to make column backgrounds extend to the bottom of the slide:

:::: {.columns fullheight="true"}
::: {.column width="40%" bg="#e8f4f8"}
**Left Column**

This background extends to the bottom of the slide content area.

- Great for split layouts
- Creates visual separation
- Professional appearance
:::

::: {.column width="60%" bg="#fff5e6"}
**Right Column**

Both columns have the same full height, regardless of content length.

The background fills the remaining vertical space on the slide.
:::
::::

**Syntax:**

```markdown
:::: {.columns fullheight="true"}
::: {.column width="40%" bg="#e8f4f8"}
Left content
:::
::: {.column width="60%" bg="#fff5e6"}
Right content
:::
::::
```

# YAML Configuration System

##

{{< v -2em >}}

**Superslides uses a minimal color system with just 3 base colors**

```yaml
# Colors (only 3!)
text-color: "#131516"       # Main text color
primary-color: "#333399"    # Primary accent (used for boxes, theorems)
secondary-color: "#9a2515"  # Secondary accent (used for warnings)
```

**How it works:**

- **Boxes**: Automatically generated from primary (simplebox) and secondary (warningbox)
- **Theorems**: All theorem environments use variations of primary-color
- **Text**: Strong emphasis uses secondary-color

## Theorem Configuration


```yaml
theorem-package: "ctheorems"     # Package selection
theorem-lang: "en"               # Language: "en" or "it"
theorem-numbering: true          # Sequential numbering (1, 2, 3...)
```

All theorem colors are automatically generated from `primary-color` with different lightness levels:

- Theorem: `primary-color.lighten(90%)`
- Lemma: `primary-color.lighten(90%)`
- Assumption: `primary-color.lighten(90%)`

## Global Box Configuration

Customize box appearance using these YAML parameters:

```yaml
# Global settings (affect all box types)
box-border-thickness: 1pt        # Border thickness
box-border-radius: 4pt           # Corner radius
box-shadow: none                 # Drop shadow (or "3pt 3pt 8pt gray")
box-title-font-size: 1.0em      # Title font size
box-title-font-weight: "bold"   # Title weight
box-body-font-size: 1.0em       # Body font size
box-body-font-weight: "regular" # Body weight
box-spacing-above: 1em          # Space above
box-spacing-below: 1em          # Space below
box-padding: 8pt                # Internal padding
```

::: {.tiny}
These settings apply globally to both simplebox and warningbox, maintaining visual consistency.
:::

# Text Sizing

## Font Size Classes

Superslides supports font size classes for both block (Div) and inline (Span) content.

### Block Syntax

```markdown
::: {.small}
This entire block is rendered in small text.
:::
```

**Result:**

::: {.small}
This entire block is rendered in small text.
:::

### Inline Syntax

```markdown
Normal text with [small inline text]{.small} in the middle.
```

**Result:**

Normal text with [small inline text]{.small} in the middle.

## Available Size Classes

| Class | Size | Example |
|-------|------|---------|
| `.tiny` | 0.6em | [Tiny text]{.tiny} |
| `.small` | 0.8em | [Small text]{.small} |
| `.smaller` | 0.8em | [Smaller text]{.smaller} |
| `.large` | 1.2em | [Large text]{.large} |
| `.larger` | 1.2em | [Larger text]{.larger} |
| `.huge` | 1.5em | [Huge text]{.huge} |

# Vertical Spacing

## The `v` Shortcode

Use `{{</* v <amount> */>}}` to add vertical space between elements.

```markdown
First paragraph.

{{</* v 2em */>}}

Second paragraph with 2em space above.
```

**Result:**

First paragraph.

{{< v 2em >}}

Second paragraph with 2em space above.

